---
title: "Hello R"
author: "Eric Lombrana"
date: "Data 2401"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT.

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

### Exercise 1

There are **1846** rows and **3** columns. The variables are **dataset**, **x-values**, and **y-values**.

### Exercise 2

Method for plotting the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Method for plotting the data in the star dataset:

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

The correlation between `x` and `y` in this dataset:

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))

```

This value compared to the dino datset is nearly identical.

### Exercise 4

Method for plotting the data in the circle dataset:

```{r plot-circle}

dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between `x` and `y` in this dataset:

```{r cor-circle}
dino_data %>%
  summarize(r = cor(x, y))

```

This value compared to the dino datset is also nearly identical.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
